\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-15 chapters/supplementary.tex
Update intro and abstract
Update supplementaries

\begin{figure}
        \centering
\begin{minipage}{0.45\textwidth}
\centering
        \includegraphics[width=0.85\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). 
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
    \end{minipage}\hfill
\begin{minipage}{0.49\textwidth}
\centering
        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
\captionof{figure}{ 
{\small Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}. }
\label{fig:edge_contraction_and_contr_graph}  }
    \end{minipage}
\end{figure}

\section{Supplementary Material}
During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, with $\tilde{V} \subseteq V$ such that node $u\in \tilde{V}$ represents the associated cluster $S_u \in \Pi$. Edges in $\tilde{E}$ are defined by adjacency-relationships between clusters and edge weights $\tilde{\cost}_{uv}$ represent inter-cluster interactions $\interact(S_u,S_v)$.

@@

@@

@@

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c | c| c | c | c | c | c}
Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
% \textbf{mean} & False & \textbf{-102739991} & {\color{Orange} 3797 } & {\color{ForestGreen} \textbf{0.0708} } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
% % mean & False & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.0715 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
% MutexWatershed & False & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.0754 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
% sum & False & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.1623 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
% % sum & False & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.1624 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
% sum & True & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.1626 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
% % sum & True & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.1574 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
% mean & True & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.1353 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
% % mean & True & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.1761 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
% max & True & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.0792 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
% max & False & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.9389 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\
% min & False & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.9263 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
% min & True & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.9221 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
    \label{tab:results_cremi_crop_C}
\end{table*}

\begin{table*}
    \centering
    \begin{subtable}[t!]{0.98\textwidth}\centering
        \begin{tabular}{c| c | c| c | c | c | c | c}
Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\

        \end{tabular}
        % \caption{Linkage criteria}
    \end{subtable} 
    \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
    \label{tab:results_cremi_crop_C}
\end{table*}

\begin{table}
    \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
        \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
\multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
 &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
\multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
 &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
\multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
 &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
\multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
 &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
\cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
% MEAN & 0.35 & True & {\color{ForestGreen} 0.3428 } & {\color{ForestGreen} 0.5493 } \\
% MEAN & 0.30 & False & {\color{ForestGreen} 0.3409 } & {\color{ForestGreen} 0.5457 } \\
% MEAN & 0.40 & - & {\color{ForestGreen} 0.3402 } & {\color{ForestGreen} 0.5502 } \\
% MEANconstr & 0.30 & False & {\color{Orange} 0.3344 } & {\color{ForestGreen} 0.5469 } \\
% MEAN & 0.45 & - & {\color{Orange} 0.3333 } & {\color{ForestGreen} 0.5438 } \\
% MEAN & 0.50 & - & {\color{Orange} 0.3255 } & {\color{ForestGreen} 0.5341 } \\
% greedyFixation & 0.50 & - & {\color{Orange} 0.3180 } & {\color{Orange} 0.5155 } \\
% MEANconstr & 0.20 & False & {\color{Orange} 0.3161 } & {\color{Orange} 0.5136 } \\
% MutexWatershed & 0.50 & - & {\color{Orange} 0.3158 } & {\color{Orange} 0.5246 } \\

>>>>

\begin{algorithm}
  \caption{\algname{} as a generalized edge contraction algorithm for signed graphs}
\hspace*{\algorithmicindent} \textbf{Input:} $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes and $M$ edges; boolean \texttt{{\color{blue}addCannotLinkConstraints}} \\
\hspace*{\algorithmicindent} \textbf{Output:} Final clustering given by union-find data structure \\
  \hspace*{\algorithmicindent} 
  \begin{algorithmic}[1]
    % \Procedure{GraphEdgeContr}{{\color{blue}bool \emph{addConstraints}}}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      \State $\tilde{\mathcal{G}}(\tilde{V},\tilde{E}) \gets \mathcal{G}(V,E,w^+,w^-)$  \Comment{Init. contracted graph}
      \State \texttt{UF} $\gets$ initUnionFind($V$) \Comment{Init. data structure representing clustering}
    %   \State PQ $\gets$ Sort $e\in E$ in descending order of $|w_e|$
        \State PQ.push$(|w_e|, e) \quad \forall e \in E $  \Comment{Init. priority queue in desc. order of $|w_e|=|w_e^+ - w_e^-|$, $\mathcal{O}(M)$}
        \State \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$ \Comment{Init. cannot-link constraints}
      % \State $E_\dagger \gets \{\}$ \Comment{Set of must-not-link edges}
    %   \State PQ.push$(e,  ) \quad \forall e \in E $  
    \State
      \While{PQ is \textbf{not} empty}
        \State $\tilde{w}, e_{uv} \gets $ PQ.popHighest() \Comment{$\mathcal{O}(\log M)$}
        \State \textbf{assert} \texttt{UF}.find($u$) $\neq$ \texttt{UF}.find($v$) \Comment{Edges in PQ always link nodes in different clusters}
        % \If{ $e_{uv} \notin E' $} 
        %     \State \textbf{continue}
        % \EndIf
        \If{({\color{ForestGreen}\textbf{$\tilde{w} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
        %   \State $u,v \gets u,v \in V' : $
        %   \State $S_u \gets S \in \Pi$ : $ u \in S$
        %   \State $S_v \gets S \in \Pi$ : $ v \in S$
          \State PQ, \texttt{canBeMerged}, $\tilde{E}$ $\gets$ \textsc{UpdateNeighbors}($u,v$)
        %   \State mergeDoubleEdges($u,v$) \Comment{Update PQ, $E_\dagger, \mathcal{G}'$}

        %   \State Update costs of double edges;
        %   \State Propagate constrained flags of double edges;
          \State $\tilde{V} \gets \tilde{V} \setminus \{ v\}$, $\quad \tilde{E} \gets \tilde{E} \setminus \{ e_{uv}\}$ \Comment{Update contracted graph}
        %   \State $ S_u \gets S_u \cup S_v$
          \State \texttt{UF}.merge($u,v$) \Comment{Merge clusters, $\mathcal{O}(\alpha(M))$}
          % \For{every new double edge}
          %   \State Delete double edges
          %   \State Insert new one with updated cost
          % \EndFor
        \ElsIf{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLinkConstraints}}}
          \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False} \Comment{Constrain the two clusters}
        \EndIf
      \EndWhile
      \State
    %   \State
      \Return Union-find structure \texttt{UF}
      % \State
    % \EndProcedure
  \hspace*{1.5cm} 
    \begin{algorithmic}[1]
    \Function{UpdateNeighbors}{$u,v$}
      % \State $\mathcal{G}'\gets \mathcal{G}(V,E^+ \cup E^-)$ \Comment{Initialize the contracted graph}
      % \State $\mathcal{N}_u = \{ t \in V' | e_{ut}\in E'  \}$; $\mathcal{N}_v = \{ t \in V' | e_{vt}\in E'  \}$ 
      \For{$t \in \mathcal{N}_v$ } \Comment{Loop over neighbors in $\tilde{\mathcal{G}}$ of deleted node $v$}
        \State $\tilde{E} \gets \tilde{E} \setminus \{e_{vt}\}$
        \State $\tilde{w}_{vt} \gets$ PQ.delete($e_{vt}$) \Comment{$\mathcal{O}(\log M)$}
        \State \texttt{canBeMerged}$[e_{ut}] \gets$ \texttt{canBeMerged}$[e_{ut}]$ \textbf{and} \texttt{canBeMerged}$[e_{vt}]$
        \If{$t \in \mathcal{N}_u$ }\Comment{$t$ is a common neighbor of $u$ and $v$}
          \State $\tilde{w}_{ut} \gets$ PQ.delete($e_{ut}$)  \Comment{$\mathcal{O}(\log M)$}
          \State PQ.push($ |f(\tilde{w}_{ut}, \tilde{w}_{vt})|, e_{ut}$) \Comment{$\mathcal{O}(\log M)$  }
        % \EndIf
        \Else
          \State $\tilde{E} \gets \tilde{E} \cup \{e_{ut}\}$
          \State PQ.push($ |\tilde{w}_{vt}|, e_{ut}$) \Comment{$\mathcal{O}(\log M)$}
        \EndIf
      \State
    %   \State
      \Return PQ, \texttt{canBeMerged}, $\tilde{E}$
    %   % \State
  \label{detailed_alg}
\begin{figure}
\begin{minipage}{0.49\textwidth}
        % \includegraphics[width=\textwidth,trim=0.1in 0.4in 0.2in 0.2in,clip]{./figs/edge_contraction.png} % left bottom right top
        \includegraphics[width=\textwidth]{./figs/edge_contraction.pdf} % left bottom right top
% \captionof{figure}{ 
% {\small Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from edge contraction are replaced by single edge with updated interaction $f(\tilde{\cost}(e_{tu}), \tilde{\cost}(e_{tv}))$, see definitions in Tab.~\ref{tab:linkage-criteria}. }
% \label{fig:edge_contraction_and_contr_graph}  }
    \end{minipage} \hfill
\begin{minipage}[T]{0.48\textwidth}
    \scriptsize
                \begin{tabular}[b]{r | l }
            \toprule
            % \multicolumn{2}{c||}{}  &   & \multicolumn{2}{c}{\textbf{Signed graphs}}  \\        
            % \cmidrule(l{.15em}){4-5}
            % \cline{4-5}
            % \multicolumn{2}{c||}{} & \textbf{Unsigned graphs} &  \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\        
            Linkage criteria & Update rule $f$ \\        
            \midrule
            Sum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \tilde{\cost}_1+\tilde{\cost}_2$} \\ 
            \makecell[r]{Absolute \\Maximum:} & \thead[l]{
            $
            f(\tilde{\cost}_1,\tilde{\cost}_2) = \begin{cases} 
            \tilde{\cost}_1 & \text{if}\,\, |\tilde{\cost}_1|>|\tilde{\cost}_2|\\
            \tilde{\cost}_2 & \text{otherwise}
             \end{cases} 
            $}
               \\ 
            \makecell[r]{Average:} & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \mathrm{weightAvg}\{ \tilde{\cost}_1, \tilde{\cost}_2 \} $}                 \\ 
            Maximum: & \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \max \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} \\
            Minimum:& \thead[l]{$f(\tilde{\cost}_1,\tilde{\cost}_2) = \min \{ \tilde{\cost}_1, \tilde{\cost}_2 \}  $} 
        \end{tabular}
    % \captionof{table}{}
    \label{tab:linkage_and_update_rules}
\end{minipage}
\caption{ 
\textbf{Left:} Example of edge contraction. First row: original graph $\mathcal{G}$; clustering $\Pi$ (gray shaded areas) with dashed edges on cut; cannot-link constraints (violet bars). Second row: contracted graph $\tilde{\mathcal{G}}_\Pi$. In step ii), edge $e_{uv}$ is contracted and node $v$ deleted from $\tilde{\mathcal{G}}_\Pi$. In step iii), double edges $e_{tu}$ and $e_{tv}$ resulting from the edge contraction are replaced by a single edge with updated interaction. \textbf{Right:} The table lists the update rules $f(\tilde{\cost}_1, \tilde{\cost}_2)$ associated to the linkage criteria of Table \ref{tab:linkage-criteria} and that are used to efficiently update the interactions between clusters. \TODO{Update figure}}
\label{fig:edge_contraction_and_contr_graph}  
\end{figure}

\section{Supplementary Material}
\subsection{Implementation details and complexity of \algname{}}

% During the agglomerative process, the interaction between adjacent clusters has to be properly updated and recomputed.  % given by the linkage criterion defined in Sec. \ref{sec:notation} and
% Given a graph $\mathcal{G}(V,E,\cost)$ and a clustering $\Pi$, we define the \emph{contracted graph} $\tilde{\mathcal{G}}_\Pi(\tilde{V}, \tilde{E}, \tilde{\cost})$, with $\tilde{V} \subseteq V$ such that node $u\in \tilde{V}$ represents the associated cluster $S_u \in \Pi$. Edges in $\tilde{E}$ are defined by adjacency-relationships between clusters and edge weights $\tilde{\cost}_{uv}$ represent inter-cluster interactions $\interact(S_u,S_v)$.

@@

\subsection{Equivalence between Mutex Watershed and \emph{Absolute Maximum} linkage}

@@

\begin{figure}
\centering
        \includegraphics[width=0.45\textwidth,trim=0.1in 0.0in 0.05in 0.0in,clip]{figs/noisy_affs_comparison.png}

    \captionof{figure}{The two figures represent the CNN predictions on a slice of the neuron segmentation CREMI challenge \cite{cremiChallenge} with and without additional noise. Blue pixels represent boundary evidence. Image a) shows the original CNN predictions, b) the merge-biased version $\tilde{F}_{+}$ and c) the split-biased version $\tilde{F}_{-}$ (see definition \ref{eq:noise_biased_predictions}). 
    %The color of each pixel represents how probable it is for it to be in the same cluster with its neighboring pixel on the right (red: same cluster; blue: different ones). 
    %Adding merge-biased noise tends to create holes in the boundaries; split-biased noise add non-existing boundaries 
    }
    \label{fig:noisy_affs}
\end{figure}

@@

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c| c | c | c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
% mean & False & True & -93152163 & {\color{Orange} 3666 } & {\color{Orange} 0.1204 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.641 } \\
% sum & False & True & -93142805 & {\color{Red} 16154 } & {\color{ForestGreen} 0.0893 } & {\color{Orange} 0.301 } & {\color{Orange} 0.514 } \\
% mean & False &  & -93072127 & {\color{Orange} 3168 } & {\color{Orange} 0.1284 } & {\color{ForestGreen} 0.234 } & {\color{Red} 0.642 } \\
% sum & True & True & -92936797 & {\color{Red} 21605 } & {\color{ForestGreen} 0.0910 } & {\color{ForestGreen} 0.293 } & {\color{Orange} 0.532 } \\
% MutexWatershed & False &  & -92704851 & {\color{ForestGreen} 632 } & {\color{Orange} 0.1347 } & {\color{ForestGreen} 0.231 } & {\color{Red} 0.751 } \\
% sum & True & False & -91444880 & {\color{Red} 26842 } & {\color{Red} 0.2085 } & {\color{Red} 0.572 } & {\color{Orange} 0.489 } \\
% mean & True & True & -90660193 & {\color{Orange} 4114 } & {\color{Orange} 0.1655 } & {\color{ForestGreen} 0.213 } & {\color{Red} 1.011 } \\
% mean & True &  & -88260595 & {\color{Orange} 4393 } & {\color{Red} 0.2017 } & {\color{ForestGreen} 0.208 } & {\color{Red} 1.155 } \\
% max & True &  & -81432464 & {\color{Red} 7759 } & {\color{Orange} 0.1653 } & {\color{ForestGreen} 0.236 } & {\color{Red} 0.792 } \\
% max & False &  & -37045939 & {\color{ForestGreen} 134 } & {\color{Red} 0.9150 } & {\color{Red} 5.691 } & {\color{ForestGreen} 0.013 } \\
% min & False &  & 213670839 & {\color{ForestGreen} 600 } & {\color{Red} 0.9330 } & {\color{ForestGreen} 0.207 } & {\color{Red} 4.880 } \\
% min & True &  & 214747429 & {\color{ForestGreen} 852 } & {\color{Red} 0.9314 } & {\color{ForestGreen} 0.202 } & {\color{Red} 4.887 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Comparison of update rules on crop of cremi sample B (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
%     \label{tab:results_cremi_crop_C}
% \end{table*}

% \begin{table*}
%     \centering
%     \begin{subtable}[t!]{0.98\textwidth}\centering
%         \begin{tabular}{c| c | c| c | c | c | c | c}
% Update rule & \makecell{Use Cannot-Link\\Constraints} & Log-costs & \makecell{Multicut objective} & Runtime (s) & ARAND & VI-merge & VI-split\\ \midrule\midrule
% mean & False &  & -102739991 & {\color{Orange} 3797 } & {\color{ForestGreen} 0.9292 } & {\color{ForestGreen} 0.286 } & {\color{ForestGreen} 0.428 } \\
% mean & False &  & -102730208 & {\color{Orange} 2562 } & {\color{ForestGreen} 0.9285 } & {\color{ForestGreen} 0.292 } & {\color{ForestGreen} 0.423 } \\
% MutexWatershed & False &  & -102313957 & {\color{ForestGreen} 830 } & {\color{ForestGreen} 0.9246 } & {\color{ForestGreen} 0.291 } & {\color{Orange} 0.471 } \\
% max & True &  & -98143342 & {\color{Red} 7153 } & {\color{ForestGreen} 0.9208 } & {\color{ForestGreen} 0.292 } & {\color{Orange} 0.496 } \\
% mean & True &  & -100279671 & {\color{Orange} 4713 } & {\color{Orange} 0.8647 } & {\color{ForestGreen} 0.265 } & {\color{Red} 0.717 } \\
% sum & True &  & -100745943 & {\color{Red} 13361 } & {\color{Orange} 0.8426 } & {\color{Orange} 0.410 } & {\color{Orange} 0.451 } \\
% sum & False &  & -101846418 & {\color{Red} 12681 } & {\color{Orange} 0.8377 } & {\color{Orange} 0.427 } & {\color{ForestGreen} 0.427 } \\
% sum & False &  & -101732952 & {\color{Red} 12287 } & {\color{Orange} 0.8376 } & {\color{Orange} 0.436 } & {\color{ForestGreen} 0.390 } \\
% sum & True &  & -101487448 & {\color{Red} 8497 } & {\color{Orange} 0.8374 } & {\color{Orange} 0.428 } & {\color{ForestGreen} 0.414 } \\
% mean & True &  & -99416111 & {\color{Orange} 3445 } & {\color{Orange} 0.8239 } & {\color{ForestGreen} 0.260 } & {\color{Red} 0.822 } \\
% min & True &  & 211183545 & {\color{ForestGreen} 692 } & {\color{Red} 0.0779 } & {\color{ForestGreen} 0.232 } & {\color{Red} 4.714 } \\
% min & False &  & 210377447 & {\color{ForestGreen} 493 } & {\color{Red} 0.0737 } & {\color{ForestGreen} 0.233 } & {\color{Red} 4.745 } \\
% max & False &  & -48601637 & {\color{ForestGreen} 102 } & {\color{Red} 0.0611 } & {\color{Red} 5.738 } & {\color{ForestGreen} 0.035 } \\

%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Comparison of update rules on crop of cremi sample C (sorted by multicut energy) \TODO{Reduce insane amount of numbers. Better put figures, leave numbers in the supplementary and only insert small table with MC, ARAND, Runtime. Invert ARAND to make it consistent with the plots} }
%     \label{tab:results_cremi_crop_C}
% \end{table*}

% \begin{table}
%     \centering
%     \begin{subtable}[t!]{0.5\textwidth}\centering
%         \begin{tabular}{M{0.1\textwidth}| c| c| c | c }
%         \thead{Update \\rule} & \thead{Use Cannot-Link\\ Constraints} & \thead{Bias \\factor $\beta$} & \thead{AP} & \thead{AP 50\%} \\ \midrule\midrule
% \multirow{2}{*}{Sum} &No & 0.55  & {\color{Orange} 0.313 } & {\color{Orange} 0.511 } \\
%  &Yes & 0.55  & {\color{Orange} 0.319 } & {\color{Orange} 0.527 } \\\midrule
% Abs. max. &- & 0.45  & {\color{Orange} 0.321 } & {\color{ForestGreen} 0.531 } \\\midrule
% \multirow{2}{*}{Mean} &No & 0.35  & {\color{ForestGreen} 0.343 } & {\color{ForestGreen} 0.552 } \\
%  &Yes & 0.25  & {\color{Orange} 0.339 } & {\color{ForestGreen} 0.548 } \\\midrule
% \multirow{2}{*}{Max} &No & 0.85 & {\color{Red} 0.243 } & {\color{Red} 0.444 } \\
%  &Yes & 0.50  & {\color{Orange} 0.325 } & {\color{ForestGreen} 0.530 } \\\midrule
% \multirow{2}{*}{Min} &No & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\
%  &Yes & 0.50  & {\color{Red} 0.000 } & {\color{Red} 0.000 } \\\midrule
% \cite{liu2018affinity} &-  & -  & {\color{ForestGreen} 0.341 } & {\color{ForestGreen} 0.547 } \\
%         \end{tabular}
%         % \caption{Linkage criteria}
%     \end{subtable} 
%     \caption{Results on cityscapes validation set (with finetuned affinities). \TODO{Reformat in the usual form, delete colors, less digits}}
%     \label{tab:results_cityscapes_full}
% \end{table}

% \begin{algorithm}[t]
%   \caption{Generalized Algorithm for Signed Graphs Agglomerative Clustering}
%    \hspace*{\algorithmicindent} \textbf{Inputs:} Graph $\mathcal{G}(V,E,w^+,w^-)$ with $N$ nodes; boolean variable {\color{blue}\texttt{addCannotLink}}  \\
%   \hspace*{\algorithmicindent} \textbf{Outputs:} Final clustering $\Pi$\\
%   \hspace*{\algorithmicindent} 
%   \begin{algorithmic}[1]

%       \State Init. clustering $\Pi=\{\{v_1\}, \ldots, \{v_N\}\}$ and contracted graph $\tilde{\mathcal{G}}_\Pi \gets \mathcal{G}$
%       \State Init. \texttt{canBeMerged}$[e] \gets$ \texttt{True} $\,\,\, \forall e\in E$
%       \State Sort edges in priority queue (PQ) in descending order of priority $|\cost_e|=|w^+_e - w^-_e|$ 
%       \State
%       \While{PQ is \textbf{not} empty}
%         \State Pop edge $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ with highest absolute interaction $|\tilde{\cost}|$
%         \If{({\color{ForestGreen}\textbf{$\tilde{\cost} > 0$}}) \textbf{and} \texttt{canBeMerged}$[e_{uv}]$}
%           \State Contract $e_{uv}$ in $\tilde{\mathcal{G}}_\Pi$ and merge the two clusters $S_u,S_v \in \Pi$
%           \For{every new pair of double edges $(e_1,e_2)$ in $\tilde{\mathcal{G}}_\Pi$}
%             % \State Get costs $\cost_1, \cost_2$ of $e_1,e_2$
%             \State Delete $e_2$ from $\tilde{\mathcal{G}}_\Pi$ and update priority of $e_1$ with rule $f(\tilde{\cost}_{e_1},\tilde{\cost}_{e_2})$ defined in Tab. \ref{tab:linkage-criteria} 
%           \EndFor
%         \EndIf
%         \If{({\color{red}\textbf{$\tilde{\cost} \leq 0$}}) \textbf{and} {\color{blue}\texttt{addCannotLink}}}
%           \State \texttt{canBeMerged}$[e_{uv}] \gets$ \texttt{False}
%         \EndIf
%       \EndWhile
%       \State
%       \Return $\Pi$
%   \end{algorithmic}
%   \label{main_alg_suppl}
% \end{algorithm}
